### 2020-12-10 Thesis-Chapter4-Tools.tex
Editorial improvements

The arguments used in the \ac{EA} debate are diverse and complex; in order to advance the \ac{EA} discussion, it would
help to organize all the arguments used in a cohesive manner. One way to organize arguments is to create \acp{argmap}.
\Acp{argmap} are graphical representations of the logical structures and relationships between statements, premises, and
conclusions. \Acp{argmap} are an outgrowth of the same research by Horst Rittel that originated the idea of
\acp{wicked-prob}. Though formal research on the technique is thin, \acp{argmap} have proven helpful in simplifying
complex arguments around \acp{wicked-prob} \cite{renton_2007} and in facilitating debate by helpfully slowing down
discussion, depersonalizing conflict, and lending structure and rhythm \cite{dutoit_hypermedia_2006}. This makes them
well suited as a tool for conducting the collaborative debate that helps problem solvers with disparate views narrow in
on a problem definition and concrete proposals on which they can agree.

@@

Threat modeling is an important step in analyzing the security at the systems level. Using models abstracts away fine
details and focuses on the architecture, processes, and dataflows in a system. Models assist in the understanding of
current systems and the prevention of problems in new systems, both of which are important when facing the prospect of
designing an \ac{EA} mechanism built on top of a complex and aging technology stack.

Threat modeling begins with the questions, ``What are you building?'' and ``What can go wrong?''
\cite{shostack_threat_2014}. Answering the first question accurately is crucial, particularly for the field of
cryptography, which hinges on precise definitions of security requirements \cite{varia_2018}. Answering the second
question depends on the types of attackers to worry about, and determines the scope of threats to be considered. ``What
are you building?'' hasn't been asked enough in the current phase of the \ac{EA} debate, and ``What can go wrong?''
cannot be faithfully answered without knowing what is being built.

\Acp{DFD} are one tool designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and
external entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data
flow, not control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is of
primary concern. \myfig{fig-dfd-dh-traditional} shows the basic elements of a \ac{DFD} of a simplified Diffie-Hellman
key exchange.

@@

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
diagram. \myfig{fig-dfd-key} contains the full set of symbols. In \mychap{chap-threatmodel} I create \acp{DFD} in this
style to analyze the threats already present and those that \ac{EA} would introduce.

>>>>

The arguments used in the \ac{EA} debate are diverse and complex. Therefore, in order to advance the \ac{EA} discussion,
it is necessary to organize the many different arguments in a cohesive manner. This thesis uses \acp{argmap} to do so.
\Acp{argmap} are graphical representations of the logical structures and relationships between statements, premises, and
conclusions. \Acp{argmap} are an outgrowth of the same research by Horst Rittel that originated the idea of
\acp{wicked-prob}. Though formal research on the technique is sparse, \acp{argmap} have proven helpful in simplifying
complex arguments around \acp{wicked-prob} \cite{renton_2007} and in facilitating debate. This is because they slow down
discussion, depersonalize conflict, and lend structure and rhythm to meetings \cite{dutoit_hypermedia_2006}. They are
therefore useful as a tool for conducting the collaborative debate that helps problem-solvers with disparate views
narrow in on a problem definition and concrete proposals on which they can agree.

@@

Threat modeling is an important step in analyzing the security at the systems level. Models abstract away fine details
and focus on the architecture, processes, and dataflows in a system. Models assist in the understanding of current
systems and the prevention of problems in new systems, both of which are important when facing the prospect of designing
an \ac{EA} mechanism built on top of a complex and aging technology stack.

Threat modeling begins with the questions, ``What are you building?'' and ``What can go wrong?''
\cite{shostack_threat_2014}. Accurately answering the first question is crucial, particularly for the field of
cryptography, which hinges on precise definitions of security requirements \cite{varia_2018}. The answer to the second
question depends on the types of attackers under consideration and determines the scope of threats to be considered.
``What are you building?'' hasn't been asked enough in the current phase of the \ac{EA} debate, and ``What can go
wrong?'' cannot be faithfully answered without knowing what is being built.

\Acp{DFD} were designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and external
entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data flow, not
control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is of primary
concern. \myfig{fig-dfd-dh-traditional} shows the basic elements of a \ac{DFD} of a simplified Diffie-Hellman key
exchange.

@@

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
diagram. \myfig{fig-dfd-key} contains the full set of symbols. \mychap{chap-threatmodel} includes \acp{DFD} in this
style to analyze the threats already present and those that \ac{EA} would introduce.

### 2020-12-10 Thesis-Chapter5-Arguments.tex
Restructure contents of background chapter
Work on DFD section and normalize captions
Spruce up title, clean up Tools chapter
Editorial improvements

\begin{sidewaysfigure}
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.contrib.pdf}
  \caption[Contributing Factors to the EA Debate]{Contributing Factors to the EA Debate}
  \label{fig-args-contrib}
\end{sidewaysfigure}

@@

% TODO: Dulimarta: Orange/green boxes for consistency? Decide when I make a key.

@@

Despite device key escrow's tractability as a technical niche of \ac{EA}, it still has a long way to go. There are few
proposals, what few there are are high level, and questions of scaling and administration have not been addressed.
However, as \ac{incrementalism}'s Lindblom and even \ac{GCHQ}'s Levy and Robinson have pointed out, focusing on specific
proposals has the opportunity to identify mutually agreeable solutions---or at least refine the problem understanding
enough that the next round of debate can be better informed.

>>>>

\begin{sidewaysfigure}
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.contrib.pdf}
  \caption{Contributing Factors to the EA Debate}
  \label{fig-args-contrib}
\end{sidewaysfigure}

@@

@@

Despite device key escrow's tractability as a technical niche of \ac{EA}, it still has a long way to go. There are few
proposals, what few there are high level, and questions of scaling and administration have not been addressed. However,
as \ac{incrementalism}'s Lindblom and even \ac{GCHQ}'s Levy and Robinson have pointed out, focusing on specific
proposals has the opportunity to identify mutually agreeable solutions---or at least refine the problem understanding
enough that the next round of debate can be better informed.
